What is an Ancestral Recombination Graph?

### 2022-02-18 paper.tex
Correct notation from eARG to gARG

\begin{figure}
\centering
\includegraphics[width=\textwidth]{illustrations/ARG_edge_annotations}
\caption{\label{fig-ancestry-resolution}
Implicit vs explicit edge annotations. (a) An eARG equivalent to the encoding
described by Griffiths can be created by setting all edges to span the full
genome, apart from edges between two recombining nodes and their recombinant
child (edge spans in bold). (b) The sample-resolved eARG, where the Hudson
simplification algorithm has shortened edge spans so that they encapsulate only
the upwards transmission of genetic material from the samples A, B, and C;
plotted line widths are proportional to the genomic span of each edge. The
example ARG used here is taken from \citet[][fig. 1]{wiuf1999recombination}.
}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{illustrations/ARG_edge_annotations}
\caption{\label{fig-ancestry-resolution}
Implicit vs explicit edge annotations. (a) An gARG equivalent to the encoding
described by Griffiths can be created by setting all edges to span the full
genome, apart from edges between two recombining nodes and their recombinant
child (edge spans in bold). (b) The sample-resolved gARG, where the Hudson
simplification algorithm has shortened edge spans so that they encapsulate only
the upwards transmission of genetic material from the samples A, B, and C;
plotted line widths are proportional to the genomic span of each edge. The
example ARG used here is taken from \citet[][fig. 1]{wiuf1999recombination}.
}
\end{figure}
